Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2023-03-14 writing/SuB-abstract/SuB-abstract.tex
fixed title

\begin{center}
	\textbf{\large%\thetitle
		Projection variability for attitude complements across entia}
\end{center}

\vspace{-.7\baselineskip}
\noindent 
	We present experimental data that the projection of the content of attitude complements \textbf{(i)} varies between entailment-canceling operators, and \textbf{(ii)} that this by-operator variation differs between attitude predicates.
	%
	The observed variability is not captured by existing theoretical accounts of projection (e.g.,
	\citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}), but suggests that an account of projection must consider interactions between predicates and operators, which cannot be fully determined based on categorical lexical classes. Instead, our results reveal a more nuanced picture of lexical semantic and pragmatic properties, which raises important questions for future research on projection.
	%

@@

	\vspace{-.5\baselineskip}
	\noindent  Current research only rarely examines differences in projectivity across these four operators, with conflicting findings.
	%
	\citet{smith_relationship_2014} found that that the content of non-restrictive relative clauses and the preparatory content of \emph{win} was more projective under conditionals than negation, whereas the projective content of epithets and the clausal complement of \emph{know} showed the opposite pattern.
	%
	\citet{karttunen_observations_1971} proposed that the CC of English factive predicates (e.g. \emph{be annoyed, regret}) projects across all four operators, whereas that of semi-factives (e.g. \emph{discover, realize, see, notice}) only projects across negation.
	%
	In contrast, \posscite{sieker_projective_2022} investigation of the projection of the CC of German attitude predicates found no significant projection variability across the four operators in \Last, regardless of predicate type. In particular, they did not find a difference between factive and semi-factive verbs, nor did they replicate \posscite{smith_relationship_2014} result for the German counterpart of `know' (\emph{wissen}).
	%
	The divergent results raise the question of whether they are due to variation between English and German or methodological differences.

@@

>>>>

\begin{center}
	\textbf{\large%\thetitle
		Projection variability of attitude complements across different operators}
\end{center}

\vspace{-.7\baselineskip}
\noindent 
	We present experimental data that the projection of the content of attitude complements \textbf{(i)} varies between entailment-canceling operators, and \textbf{(ii)} that this by-operator variation differs between attitude predicates.
	%
	The observed variability is not captured by existing theoretical accounts of projection
	(e.g., \citealt{heim_projection_1983,van_der_sandt_presupposition_1992,abrusan_predicting_2011,schlenker_triggering_2021}), but suggests that an analysis must consider interactions between predicates and operators, which cannot be fully determined by lexical classes. Instead, our results reveal a more nuanced picture of lexical semantic and pragmatic properties, which raises important questions for future research on projection.
	%

@@

	\vspace{-.5\baselineskip}
	\noindent  Current research only rarely examines differences in projectivity across these four operators, with conflicting findings.
	%
	\citet{smith_relationship_2014} found that that the content of non-restrictive relative clauses and the preparatory content of \emph{win} was more projective under conditionals than negation, whereas the projective content of epithets and the clausal complement of \emph{know} showed the opposite pattern.
	%
	\citet{karttunen_observations_1971} proposed that the CC of English factive predicates (e.g. \emph{be annoyed, regret}) projects across all four operators, whereas that of semi-factives (e.g. \emph{discover, realize, see, notice}) only projects across negation.
	%
	In contrast, \posscite{sieker_projective_2022} investigation of the projection of the CC of German attitude predicates found higher projectivity under negation than other operators (e.g. modals), but no interaction with predicate type. In particular, they did not find a difference between factive and semi-factive verbs, nor did they replicate \posscite{smith_relationship_2014} result for the German counterpart of `know' (\emph{wissen}).
	%
	The divergent results raise the question of whether they are due to variation between English and German or methodological differences.

@@

	% the projection of the complement clause (CC) of 20 attitude predicates was measured in four sets of experiments: polar questions (Exps. 1), negation (Exps. 2), perhaps (Exps. 3), and conditional antecedents (Exps. 4). Each set had three experiments, using different measures. Participants judged whether the speaker was certain of the CC and responded on a slider from 0 to 1. Each participant saw all 20 attitude predicates paired with a unique content under one operator. Data was analyzed from 2,682 self-reported native speakers of American English recruited on Prolific or Amazon’s MT platform. Factive predicates were expected to receive high projection ratings under all four operators, while semi-factive predicates were expected to have high ratings under negation and lower ratings under the other operators.
